Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-11-26 patchy-selection-paper.tex
example sim plots

The agreement is reasonable for both

\begin{figure}[ht!]
  \begin{center}
      % made in analyze-sims.R
      \includegraphics{times-predicted-observed}
  \end{center}
  \caption{
      \textbf{(left)} 
      Time until adaptation by mutation in an isolated patch for different parameter combinations,
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:mutrate} (horizontal axis).
      \textbf{(right)} 
      Time until adaptation by migration from an already occupied patch to a new patch,
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:migrate} (horizontal axis).
      For each,
      parameter combinations and numbers of simulations are in supplemental tables \ref{stab:migration_params} and \ref{stab:mutation_params};
      shown are the median (points) and interquartile range (lines)
      of the time until the patch had at least 100 adapted individuals,
      for each unique parameter combination.
  }   \label{fig:sim_times}
\end{figure}

%%%%%%%%%
\subsection{Comparison to simulation}
\label{ss:comparison_to_sims}

We used the simulations describe above to test the theory,
etcetera.

@@

>>>>

The agreement is reasonable for both.
The theoretical value $1/\mutrate$ underestimates the mean time to mutation
by a factor of around 2 that depends increases with $s_m$.
This is to be expected for two reasons:
First, we compute the time to reach 100 $B$ alleles, while theory predicts
the time until the the progenitor of those 100 $B$ alleles arose.
Second, the expression for $\mutrate$ neglects effects near the boundary of the patch,
and the larger $s_m$ is, 
the harder it is for mutations that arise near the edge of the patch to establish.
The theoretical values $1/\migrate$ again has a margin of error of a factor of about 2,
with the exception of the weakest disadvantage off the patch, $s_m=10^{-4}$,
which adapt much more quickly than predicted by theory.
However, these simulations fall outside the region where we expect the model to do well,
since $R < \sigma/\sqrt{s_m} \approx 100$.
A glance at SUPP FIGURE XXX reveals more:
since selection is weaker than Wright's effective neighborhood size ($s_m < 1/2 \rho \sigma \le 1/8000$), 
local drift is stronger than selection,
and local migration-selection balance looks very little like the deterministic equilibirium.

\begin{figure}[ht!]
  \begin{center}
      % made in analyze-sims.R
      \includegraphics{times-predicted-observed}
  \end{center}
  \caption{
      \textbf{(left)} 
      Time until adaptation by mutation in an isolated patch for different parameter combinations,
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:mutrate} (horizontal axis).
      \textbf{(right)} 
      Time until adaptation by migration from an already occupied patch to a new patch,
      as observed in simulations (vertical axis),
      and as predicted from equation~\eqref{eqn:migrate}, with $C=5$ (horizontal axis).
      For each,
      parameter combinations and numbers of simulations are in supplemental tables \ref{stab:migration_params} and \ref{stab:mutation_params};
      shown are the median (points) and interquartile range (lines)
      of the time until the patch had at least 100 adapted individuals,
      for each unique parameter combination.
  }   \label{fig:sim_times}
\end{figure}

@@

% sm=0.1
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/18885-r1-501-sb0.01-sm-0.1-N1200-pophistory-run}.pdf}
    \includegraphics{{example-sims/56325-r1-501-sb0.01-sm-0.1-N600-pophistory-run}.pdf}
    \includegraphics{{example-sims/28432-r1-501-sb0.01-sm-0.1-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.1$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.01
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/43099-r1-501-sb0.01-sm-0.01-N1200-pophistory-run}.pdf}
    \includegraphics{{example-sims/69787-r1-501-sb0.01-sm-0.01-N600-pophistory-run}.pdf}
    \includegraphics{{example-sims/11821-r1-501-sb0.01-sm-0.01-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.01$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.001
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/59611-r1-501-sb0.01-sm-0.001-N1200-pophistory-run}.pdf}
    \includegraphics{{example-sims/93713-r1-501-sb0.01-sm-0.001-N600-pophistory-run}.pdf}
    \includegraphics{{example-sims/29850-r1-501-sb0.01-sm-0.001-N50-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}

% sm=0.0001
\begin{figure}
  \begin{center}
    \includegraphics{{example-sims/15449-r1-501-sb0.01-sm-1e-04-N1600-pophistory-run}.pdf}
    \includegraphics{{example-sims/5582-r1-501-sb0.01-sm-1e-04-N400-pophistory-run}.pdf}
    \includegraphics{{example-sims/24639-r1-501-sb0.01-sm-1e-04-N25-pophistory-run}.pdf}
  \end{center}
  \caption{
    Randomly chosen simulations with $s_m=0.001$, $\sigma\approx 1$, and $\rho$ varying.
    On the left of each is a space-time heatmap of the local frequency of $B$ alleles;
    and on the right are twenty-five curves showing the frequencies of $B$ at evenly spaced time points
    (i.e.\ each line represents a vertical slice through the plot on the left).
  } \label{sfig:sims_1}
\end{figure}
